Resumé title

### 2017-06-27 paper/coverletter.tex
no the?

The document has been formatted with \LaTeX\ article class.
The summary is 286 words long, and the main text has $\approx 1424$ words,
29 references,
and two single-panel figures and one table, which should fit the page limit
of a Nature Letter.
We also include six extended data figure that will help the interested readers
get the full context, as well as supplementary material discussing several
aspects of the main text.

>>>>

The document has been formatted with \LaTeX\ article class.
The summary is 286 words long, and the main text has $\approx 1424$ words,
29 references,
and two single-panel figures and one table, which should fit the page limit
of a Nature Letter.
We also include six extended data figure that will help interested readers
get the full context, as well as supplementary material discussing several
aspects of the main text in more detail.
